\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model and main results}

@@

\begin{definition}[Model parameterization and assumptions]
    \label{def:model_setup}
    For each $\theta \ge 0$,
    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
    be the continuous-time measure-valued Markov process described above
    with birth rates, establishment probabilities, and death rates
    determined as follows.
    Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
    are bounded, uniformly continuous functions
    from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
    Furthermore, suppose $r_\theta$ takes values in $[0, 1]$
    and has uniformly bounded second derivatives,
    and that $(x, m) \mapsto m^2 \gamma(x, m)$ is unformly bounded.
    Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
    with $\epsilon_r < \epsilon_\gamma - 1/\theta$.
    Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
    and define
    \begin{align}
        \mu(x, \eta)
        =
        r(x, \smooth{r} \eta(x))
        \gamma(\smooth{\gamma} \eta(x))
        - \frac{1}{\theta}
        F(x, \smooth{F} \eta(x)) .
    \end{align}
    Let $N$ be a positive number determined by $\theta$.
    When the state of the process is $\eta$,
    offspring of mass $1/N$ are produced at location $x$
    with rate $\theta \gamma(x, \smooth{\gamma} \eta(x)) N \eta(dx)$
    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta(dx)$,
    (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
    Offspring disperse to a location offset from the parent's location
    by an independent Gaussian with mean $\meanq/\theta$
    and covariance matrix $\covq / \theta$;
    an offspring at $x$ establishes instantaneously
    with probability $r(x, \smooth{r} \eta(x))$, or else dies.
\end{definition}

@@

\paragraph{Remark:}
An equivalent way to describe the model
would be to say that an individual at $x$ gives birth at rate
$$
    \gamma(x, \smooth{\gamma} \eta(x))
    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x, dy)
    :=
    \frac{
        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{\theta \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

    The sequence of stochastic processes
    $(\eta^\theta_t)_{t \geq 0}$
    converges along subsequences in distribution as $\theta \to \infty$
    to a measure-valued process $(\eta_t)_{t \geq 0}$
    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
    \begin{align} \label{eqn:mgale_problem}
        M_t
        &:=
        \langle f(x), \eta_t(dx) \rangle
        -
        \langle f(x), \eta_0(dx) \rangle
        \\ & \qquad
        -
        \int_0^t \big\langle
            \gamma(x, \smooth{\gamma} \eta_s(x))
            \mathcal{B}\left(
                f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot))
            \right)(x)
            +
            f(x)
            F(x, \smooth{F} \eta_s(x)),
            \eta_s(dx)
        \big\rangle ds,
    \end{align}
    is a martingale.
    The quadratic variation of $M_t$ is given by 
    \begin{align} \label{eqn:mgale_variation}
        [ M ]_t
        =
        \delta
        \int_0^t
        \big\langle
            \gamma\left( x, \smooth{\gamma} \eta_s(x) \right)
            r\left(x, \smooth{r} \eta_s(x) \right)
            f^2(x),
            \eta_s (dx)
        \big\rangle ds. 
    \end{align}
    In other words, the limit is a measure-valued process with non-local interactions.
    Furthermore, if $\delta = 0$ the limit is deterministic.
\end{theorem}

@@

We write $\Pgen^\theta$
for the generator of the scaled population process $\eta$ acting
on test functions of the form 
$$
    F( \langle f, \eta\rangle )
    =
    F \left( \int f(x)\eta(dx) \right),
$$
where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
$F \in C^\infty ([0,\infty))$.
Recall that $N \to \infty$ along with $\theta$,
although we don't remind the reader with extra superscripts.

@@

Consider first the mean measure. For a suitable 
(smooth, compactly supported) test function $f$, we find
\begin{multline}
\label{mean measure}
{\cal L}^{(\theta, N)}\langle f,\eta\rangle=
\lim_{\delta t\downarrow 0}\frac{1}{\delta t}
\IE\left[\left.\langle f,\eta_{\delta t}\rangle -
\langle f, \eta\rangle \right|\eta_0=\eta
\right]\\
=\theta\int\int f(z)r_\theta(z,\eta)q_\theta(x,dz)
\gamma_\theta(x,\eta)
\eta(dx)-\theta\int f(x)\mu_\theta(x,\eta)
\eta(dx).
\end{multline}
The first term is the increment in $\langle f,\eta\rangle$
resulting from a birth event (recalling that
we don't kill the parent) integrated against the rate of such events,
and the second reflects death events.
In both terms, the 
rate of events has a factor of $N$ (because events happen at a rate 
proportional to the number of individuals, whereas $\eta$ is
the scaled population mass) which is offset by the fact that  
the birth or loss of a single 
individual at the point $y$, say, changes $\langle f,\eta\rangle$
by $f(y)/N$.

We use the fact that $\int q_\theta(x,dz)=1$ to rewrite~(\ref{mean measure})
as 
\begin{multline}
\label{rewritten mean measure}
\int\left(\int \theta \left(
f(z)r_\theta(z,\eta)- f(x)r_\theta(x,\eta)\right)
q_\theta(x,dz)\right)
\gamma_\theta(x,\eta)
\eta(dx)
\\
+\int\theta\int f(x)\Big(r_\theta(x,\eta)
\gamma_\theta(x,\eta)
-\mu_\theta(x,\eta)\Big)
\eta(dx).
\end{multline}
Suppose that $\eta\to\Xi$, a measure on $\IR^d$,
in the scaling limit, then we see that we can 
let $\theta\rightarrow\infty$ in~(\ref{rewritten mean measure})
under the assumptions that
\begin{eqnarray}
r_\theta(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
r(x,\Xi)\\
\gamma_\theta(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
\gamma(x,\Xi)\\
\int\theta \Big(r(z,\eta)f(z)-
r(x,\eta)f(x)\Big)q_\theta(x,dz) 
&\stackrel{\theta\to\infty}{\longrightarrow}& 
\Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x);\\
\theta \Big(r_\theta(x,\eta)\gamma_\theta (x,\eta)
-\mu_\theta (x,\eta)\Big)
 &\stackrel{\theta\to\infty}{\longrightarrow}& 
F(x,\Xi),
\label{near critical}
\end{eqnarray}
where $\Delta$ denotes the Laplacian.
The last condition reflects the `near-critical' branching. Note that
there is a slight mismatch between the locations at which we are 
measuring birth and death rates, because in~(\ref{near critical})
the establishment probability is 
measured at $x$ rather than at the point where juveniles fall. 
This condition also differs from the assumption that
we use in~\S\ref{scalings with levels} to guarantee convergence of the 
processes with levels in our lookdown 
constructions, see~(\ref{lookdown blambda}). 
Under mild
regularity conditions on $r$ (which we certainly need to have sensible 
limiting models) the conditions are equivalent.

@@

When an individual at the point $x$ gives birth, the total number of
mature offspring is Poisson with parameter
$$\gamma_\theta(x,\eta)\int 
r_{\theta}(y,\eta) q_{\theta}(x, dy)
=\gamma_\theta(x,\eta)p_\theta(x,\eta).$$
Offspring that survive to maturity are distributed about the parent
according to 
$$\overline{q}_\theta(x,\eta,dy):=
\frac{r_{\theta}(y,\eta)q_\theta(x,dy)} 
{\int r_{\theta}(z,\eta)q_\theta(x,dz)}. 
$$
Writing $X(x)$ for the increment to $\langle f, \eta\rangle$
due to a single mature offspring of an individual at $x$, 
and $P(x)$ for the (Poisson) number of mature
offspring in such an event, the variance of the increment to 
$\langle f, \eta\rangle$
resulting from a birth event at $x$ is $\IE[P(x)]\mathtt{var}(X(x))
+\mathtt{var}(P(x))\IE[X(x)]^2=\IE[P]\IE[X(x)^2]$. 
Since, in this notation, conditional on the value of $\eta$
immediately before the event,
$$\IE[X(x)^2]=\int
\frac{1}{N^2}f^2(y) \overline{q}_\theta(x,\eta,dy),$$
and
$$\IE[P(x)]=
\gamma_\theta (x,\eta) \int 
r_{\theta}(z,\eta)q_\theta(x,dz),$$ 
the contribution to the quadratic variation from birth events, which
occur at rate $\theta$ per individual 
(so $N\theta |\eta|$ overall), is
$$\langle N\theta \gamma_\theta(x,\eta)
\int \frac{1}{N^2}f^2(y)r_{\theta}(y,\eta)
q_\theta(x,dy) 
,\eta(dx)\rangle.$$
The increment in $\langle f, \eta\rangle$ resulting from 
the death of an individual at $x$ is $f(x)/N^2$, and so combining with the 
above, the second order term in the generator takes the form
$$F''(\langle f,\eta\rangle)
\frac{1}{2}N\theta \left\{
\langle \gamma_\theta(x,\eta)
\int \frac{1}{N^2}f^2(y)r_\theta(y,\eta)q_\theta(x,dy) 
,\eta(dx)\rangle
+\langle \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
,\eta(dx)\rangle\right\}.
$$
The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
${\mathcal O}(\theta/N^2)$.

@@

Now we
will present a lookdown construction for $(\overline{\eta}^{\epsilon,\theta,N}(t))_{t \geq 0}$ stated in Definition \ref{Def: Rescaled Models}
in the spirit of~\cite{kurtz/rodrigues:2011}. 
The key benefit of working in such a framework is that
we shall be able to preserve the notion of individuals, and in particular their genealogies, when we pass to the limit. Our notation will follow a standard pattern.

% % % % % % % % % % % % % % % %
\subsection*{Prelimit Models and Notation}\label{Prelimit Models and Notation Section}

In the prelimiting models each individual in the population will be assigned a 
`level' from $[0,\lambda]$. We also let $\lambda$ takes on the role of $N$ in \S \ref{sec: model and results}, i.e. each individual has mass $1/\lambda$ in the scaling limit. Speed is once again scaled by $\theta$ and local radius by $\varepsilon(\theta)$.\\
A state of the discrete population model will be of the form $\eta=\sum\delta_{(x,u)}$, where $x$ denotes the  
spatial location of an individual, and $u$ is its level. Just as we did in \S\ref{prelimiting spatial model}, we shall
abuse notation and treat $\eta$ both as a set and as a counting
measure. The population of \S\ref{prelimiting spatial model}
is recovered as $\overline{\eta}=\frac{1}{\lambda}\sum_{(x,u)\in\eta}\delta_x$, i.e. $\overline{\eta}$ is the spatial projection of our spatial-level model $\eta$. 
Conditional on $\overline{\eta}$, the levels of individuals in 
the population will be independent, uniformly distributed random variables
on $[0,\lambda]$. All of this can be found in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
Test functions for this enriched process take the form
\begin{equation}
\label{test functions}
f(\eta)=\prod_{(x,u)\in\eta}g(x,u)=\exp\left(\int\log g(x,u)\eta(dx, du)\right),
\end{equation}
where $g(x,u)$ is differentiable in $u$ and 
smooth in $x$. Moreover, $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$, and 
$g(x,u)\equiv 1$ for $u\geq \lambda$.

@@

% % % % % % % % % % % % % % % %
\subsection*{Generator of the Scaled Lookdown Model}

In the notation of \S\ref{heuristics}, we now write down the 
generator of the scaled population model with levels where 
$\lambda$ is the scaling factor of the mass of an individual, $\theta(\lambda)$ is the scaling factor for time and the level of an individual particle must be in $[0,\lambda]$.  
Recall that we only track the adult population; maturity, if achieved, is 
instantaneous. Furthermore, at rate $\theta\gamma_{\theta}(x, \overline{\eta})$ a parent gives birth to a single juvenile offspring.

We should consider an initial population of $O(\lambda)$ many particles with levels uniformly distributed between $[0, \lambda]$. We write $(\eta^{\theta, \lambda}(t))_{t \geq 0}$ for our population at the $\theta$th stage of rescaling. To recover the scaling of \S\ref{sec: model and results} we scale the empirical distribution of particles alive with a factor of $1/\lambda$, so we write $$\overline{\eta}^{\theta, \lambda}(t)=\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta \\ U(t) < \lambda}} \delta_{X(t)}.$$ 
From here onwards we write $\eta$ to be the particle systems with levels while $\overline{\eta}$ is the normalised empirical distribution. An individual of the population with state $\eta$ living at spatial location $x$ produces
one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$, where
$$\gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta})=\gamma_\theta(x,\overline{\eta})
\int r_\theta (y, \overline{\eta})q_\theta(x,dy).
$$
The location of this offspring is given by
the distribution 
\[ q^{\mathfrak{m}}_\theta(x,\overline{\eta},dy) = \frac{r(y,\overline{\eta}) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\overline{\eta}) q_{\theta}(x,dy)}. \] In the lookdown version of our model, the individual $(x,u)\in\eta^{\theta, \lambda}$ gives
birth to an offspring at rate 
$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$. 
(Averaging
over the distribution of the
level $u$ we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$.)

A new level $u_1$ is sampled independently and
uniformly from $[u,\lambda]$, and the parent and the offspring 
are assigned in random order to the  levels $\{u, u_1\}$. This random assignment of levels to child and offspring ensures that conditional on $\overline{\eta}$, the levels assigned to individuals are i.i.d. uniform random variables. Otherwise, the levels of the initial population would be lower than those of the descendants.\\
Evidently this mechanism increases the proportion of individuals with
higher levels. To restore the property that,
conditional
on $\overline{\eta}$, the intensity of
levels is conditionally uniform, we impose that 
the level associated with
$(x,u)\in\eta$ evolves
according to the differential equation
$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta}) 
\left\{\lambda^{-1}(\lambda -v)^{2}
-(\lambda -v)\right\}.$$

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model and main results}
    \label{sec: Model and main results}

@@

\begin{definition}[Model parameterization and assumptions]
    \label{def:model_setup}
    For each $\theta \ge 0$,
    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
    be the continuous-time measure-valued Markov process described above
    with birth rates, establishment probabilities, and death rates
    determined as follows.
    Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
    are bounded, uniformly continuous functions
    from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
    Furthermore, suppose $r$ takes values in $[0, 1]$
    and has uniformly bounded second derivatives,
    and that $(x, m) \mapsto m^2 \gamma(x, m)$ is unformly bounded.
    Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
    with $\epsilon_r < \epsilon_\gamma - 1/\theta$.
    Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
    and define
    \begin{align}
        \mu(x, \eta)
        =
        r(x, \smooth{r} \eta^{\theta}(x))
        \gamma(\smooth{\gamma} \eta^{\theta}(x))
        - \frac{1}{\theta}
        F(x, \smooth{F} \eta^{\theta}(x)) .
    \end{align}
    Let $N$ be a positive number determined by $\theta$.
    When the state of the process is $\eta$,
    offspring of mass $1/N$ are produced at location $x$
    with rate $\theta \gamma(x, \smooth{\gamma} \eta^{\theta}(x)) N \eta^{\theta}_s(dx)$
    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta^{\theta}_s(dx)$,
    (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
    Offspring disperse to a location offset from the parent's location
    by an independent Gaussian with mean $\meanq/\theta$
    and covariance matrix $\covq / \theta$;
    an offspring at $x$ establishes instantaneously
    with probability $r(x, \smooth{r} \eta^{\theta}(x))$, or else dies.
\end{definition}

We will now define $(\eta^{\theta}(t))_{t \geq 0}$
explicitly as a solution to a Martingale problem.

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
&     M^{\theta}_t(f)\\
:=&  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        f(z)r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int 
f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned}
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

\paragraph{Remark:}
An equivalent way to describe the model
would be to say that an individual at $x$ gives birth at rate
$$
    \gamma(x, \smooth{\gamma} \eta^{\theta}(x))
    \int r(x, \smooth{r} \eta^{\theta}(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x, dy)
    :=
    \frac{
        r(y, \smooth{r} \eta^{\theta}(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{\theta \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{\theta}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

    The sequence of stochastic processes
    $(\eta^\theta_t)_{t \geq 0}$
    converges along subsequences in distribution as $\theta \to \infty$
    to a measure-valued process $(\eta_t)_{t \geq 0}$
    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
    \begin{align} \label{eqn:mgale_problem}
        M_t
        &:=
        \langle f(x), \eta_t(dx) \rangle
        -
        \langle f(x), \eta_0(dx) \rangle
        \\ & \qquad
        -
        \int_0^t \big\langle
            \gamma(x, \smooth{\gamma} \eta^{\theta}_{s}(x))
            \mathcal{B}\left(
                f(\cdot) r(\cdot, \smooth{r} \eta^{\theta}_{s}(\cdot))
            \right)(x)
            +
            f(x)
            F(x, \smooth{F} \eta^{\theta}_{s}(x)),
            \eta^{\theta}_{s}(dx)
        \big\rangle ds,
    \end{align}
    is a martingale.
    The quadratic variation of $M_t$ is given by 
    \begin{align} \label{eqn:mgale_variation}
        [ M ]_t
        =
        \delta
        \int_0^t
        \big\langle
            \gamma\left( x, \smooth{\gamma} \eta^{\theta}_{s}(x) \right)
            r\left(x, \smooth{r} \eta^{\theta}_{s}(x) \right)
            f^2(x),
            \eta^{\theta}_{s} (dx)
        \big\rangle ds. 
    \end{align}
    In other words, the limit is a measure-valued process with non-local interactions.
    Furthermore, if $\delta = 0$ the limit is deterministic.
\end{theorem}

@@

We write $\Pgen^\theta$
for the generator of the scaled population process $\eta$ acting
on test functions of the form 
$$
    F( \langle f, \eta\rangle )
    =
    F \left( \int f(x)\eta^{\theta}_s(dx) \right),
$$
where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
$F \in C^\infty ([0,\infty))$.
Recall that $N \to \infty$ along with $\theta$,
although we don't remind the reader with extra superscripts.

@@

Consider first the mean measure. For a suitable 
(smooth, compactly supported) test function $f$, we find
\begin{multline}
\label{mean measure}
{\cal L}^{(\theta, N)}\langle f,\eta\rangle=
\lim_{\delta t\downarrow 0}\frac{1}{\delta t}
\IE\left[\left.\langle f,\eta_{\delta t}\rangle -
\langle f, \eta\rangle \right|\eta_0=\eta
\right]\\
=\theta\int\int f(z)r(z,\eta)q_\theta(x,dz)
\gamma(x,\eta)
\eta^{\theta}_s(dx)-\theta\int f(x)\mu(x,\eta)
\eta^{\theta}_s(dx).
\end{multline}
The first term is the increment in $\langle f,\eta\rangle$
resulting from a birth event (recalling that
we don't kill the parent) integrated against the rate of such events,
and the second reflects death events.
In both terms, the 
rate of events has a factor of $N$ (because events happen at a rate 
proportional to the number of individuals, whereas $\eta$ is
the scaled population mass) which is offset by the fact that  
the birth or loss of a single 
individual at the point $y$, say, changes $\langle f,\eta\rangle$
by $f(y)/N$.

We use the fact that $\int q_\theta(x,dz)=1$ to rewrite~(\ref{mean measure})
as 
\begin{multline}
\label{rewritten mean measure}
\int\left(\int \theta \left(
f(z)r(z,\eta)- f(x)r(x,\eta)\right)
q_\theta(x,dz)\right)
\gamma(x,\eta)
\eta^{\theta}_s(dx)
\\
+\int\theta\int f(x)\Big(r(x,\eta)
\gamma(x,\eta)
-\mu(x,\eta)\Big)
\eta^{\theta}_s(dx).
\end{multline}
Suppose that $\eta\to\Xi$, a measure on $\IR^d$,
in the scaling limit, then we see that we can 
let $\theta\rightarrow\infty$ in~(\ref{rewritten mean measure})
under the assumptions that
\begin{eqnarray}
r(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
r(x,\Xi)\\
\gamma(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
\gamma(x,\Xi)\\
\int\theta \Big(r(z,\eta)f(z)-
r(x,\eta)f(x)\Big)q_\theta(x,dz) 
&\stackrel{\theta\to\infty}{\longrightarrow}& 
\Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x);\\
\theta \Big(r(x,\eta)\gamma (x,\eta)
-\mu (x,\eta)\Big)
 &\stackrel{\theta\to\infty}{\longrightarrow}& 
F(x,\Xi),
\label{near critical}
\end{eqnarray}
where $\Delta$ denotes the Laplacian.
The last condition reflects the `near-critical' branching. Note that
there is a slight mismatch between the locations at which we are 
measuring birth and death rates, because in~(\ref{near critical})
the establishment probability is 
measured at $x$ rather than at the point where juveniles fall. 
This condition also differs from the assumption that
we use in~\S\ref{scalings with levels} to guarantee convergence of the 
processes with levels in our lookdown 
constructions, see~(\ref{lookdown blambda}). 
Under mild
regularity conditions on $r$ (which we certainly need to have sensible 
limiting models) the conditions are equivalent.

@@

When an individual at the point $x$ gives birth, the total number of
mature offspring is Poisson with parameter
$$\gamma(x,\eta)\int 
r(y,\eta) q_{\theta}(x, dy)
=\gamma(x,\eta)p_\theta(x,\eta).$$
Offspring that survive to maturity are distributed about the parent
according to 
$$\overline{q}_\theta(x,\eta,dy):=
\frac{r(y,\eta)q_\theta(x,dy)} 
{\int r(z,\eta)q_\theta(x,dz)}. 
$$
Writing $X(x)$ for the increment to $\langle f, \eta\rangle$
due to a single mature offspring of an individual at $x$, 
and $P(x)$ for the (Poisson) number of mature
offspring in such an event, the variance of the increment to 
$\langle f, \eta\rangle$
resulting from a birth event at $x$ is $\IE[P(x)]\mathtt{var}(X(x))
+\mathtt{var}(P(x))\IE[X(x)]^2=\IE[P]\IE[X(x)^2]$. 
Since, in this notation, conditional on the value of $\eta$
immediately before the event,
$$\IE[X(x)^2]=\int
\frac{1}{N^2}f^2(y) \overline{q}_\theta(x,\eta,dy),$$
and
$$\IE[P(x)]=
\gamma (x,\eta) \int 
r(z,\eta)q_\theta(x,dz),$$ 
the contribution to the quadratic variation from birth events, which
occur at rate $\theta$ per individual 
(so $N\theta |\eta|$ overall), is
$$\langle N\theta \gamma(x,\eta)
\int \frac{1}{N^2}f^2(y)r(y,\eta)
q_\theta(x,dy) 
,\eta^{\theta}_s(dx)\rangle.$$
The increment in $\langle f, \eta\rangle$ resulting from 
the death of an individual at $x$ is $f(x)/N^2$, and so combining with the 
above, the second order term in the generator takes the form
$$F''(\langle f,\eta\rangle)
\frac{1}{2}N\theta \left\{
\langle \gamma(x,\eta)
\int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
,\eta^{\theta}_s(dx)\rangle
+\langle \mu(x,\eta)\frac{1}{N^2}f^2(x) 
,\eta^{\theta}_s(dx)\rangle\right\}.
$$
The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
${\mathcal O}(\theta/N^2)$.

@@

Now we will present a lookdown construction for $(\eta^{\theta}(t))_{t \geq 0}$
stated in Definition \ref{Def: Rescaled Models} in the spirit of~\cite{kurtz/rodrigues:2011}. 
The key benefit of working in such a framework is that
we shall be able to preserve the notion of individuals,
and in particular their genealogies,
when we pass to the limit.
Our notation will follow a standard pattern.

% % % % % % % % % % % % % % % %
\subsection*{Lookdown Representation and Notation}
\label{sec: Lookdown Representation and Notation}

In the prelimiting models,
each individual in the population
will be assigned a `level' from $[0,\lambda]$.

A state of the discrete population model will be of the form $\xi=\sum\delta_{(x,u)}$,
where $x$ denotes the spatial location
of an individual, and $u$ is its level.
We shall abuse notation and treat $\xi$ both as a set and as a counting measure.
The spatial population described in \S \ref{sec: Model and main results} is recovered as
$$\eta=\frac{1}{\lambda}\sum_{(x,u)\in\xi}\delta_x,$$
i.e. $\eta$ is the re-scaled spatial projection of our spatial-level model $\xi$. 
Conditional on the spatial population $\eta$,
the levels of individuals in the population
will be independently and uniformly distributed
on $[0,\lambda]$.
Similar lookdown constructions can be found in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
Test functions for this enriched process take the form
\begin{equation}
\label{test functions}
f(\xi)=\prod_{(x,u)\in \xi}g(x,u)=\exp\left(\int \log g(x,u)\xi(dx, du)\right),
\end{equation}
where $g(x,u)$ is differentiable in $u$ and 
smooth in $x$.
Moreover, $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$,
and $g(x,u)\equiv 1$ for $u\geq \lambda$.

@@

% % % % % % % % % % % % % % % %
\subsubsection*{Generator of the Lookdown Model}

We now write down the generator of
the scaled population model with levels where 
$\lambda$ is the scaling factor of the mass of an individual,
$\theta(\lambda)$ is the scaling factor for time,
and the level of an individual particle must be in $[0,\lambda]$.
Recall that we only track the adult population; maturity, if achieved, is instantaneous.
Furthermore, at rate $\theta\gamma(x, \eta)$,
a parent gives birth to a single juvenile offspring.

We should consider an initial population of $O(\lambda)$ many particles with levels
uniformly distributed between $[0, \lambda]$.
We write $(\xi^{\theta, \lambda}(t))_{t \geq 0}$
for our population at the $\theta$-th stage of rescaling.
To recover the scaling in \S\ref{sec: Model and main results},
we scale the empirical distribution of particles with a factor of $1/\lambda$,
so we write
$$\eta^{\theta, \lambda}_t:=\frac{1}{\lambda}\xi^{\theta, \lambda}_t(dx \times [0,\lambda])=
\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \xi \\ U(t) < \lambda}} \delta_{X(t)}.$$ 
From here onwards,
we write $\xi$ to be the particle systems with levels,
while $\eta$ is the normalised empirical distribution.
An individual in the spatial population $\eta$ living at spatial location $x$
produces one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)$, where
$$\gamma^{\mathfrak{m}}_{\theta}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q_\theta(x,dy).$$

The location of this offspring is given by
the distribution 
\[ q^{\mathfrak{m}}_\theta(x,\eta,dy) = \frac{r(y,\eta) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q_{\theta}(x,dy)}. \]

In the lookdown version of our model,
the individual $(x,u)\in \xi^{\theta, \lambda}$
gives birth to an offspring at rate 
$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$. 
(Averaging over the distribution of the
level $u$,
we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$.)

A new level $u_1$ is sampled independently and
uniformly from $[u,\lambda]$,
and the parent and the offspring are assigned in random order to the  levels $\{u, u_1\}$.
This random assignment of levels to parent
and offspring ensures that conditional on $\eta$,
the levels assigned to individuals are i.i.d.
uniform random variables.
Otherwise, the levels of the initial population would be lower than those of the descendants.

Evidently this mechanism increases the proportion
of individuals with higher levels.
To restore the property that,
conditional on $\eta$,
the intensity of levels is conditionally uniform,
we impose that 
the level associated with $(x,u)\in\eta$
evolves according to the differential equation
$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
\left\{\lambda^{-1}(\lambda -v)^{2}
-(\lambda -v)\right\}.$$
